---
title: "Alcohol vs Seat choice"
author: "Tania Boror"
date: "02/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
Our Goal is to answer this question: Is there a difference between the alcohol consumed between the row you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```


This box plot shows that the heavy drinkers are most likely to sit in the back. 


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```


People that sit in the back drink 3 times more than the those that sit in the middle.   

## Inferential Tests
# Inferential

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
We reject the null hypothesis because the p value is so small that it is unlikely that alcohol consumption in all three seats are the same.


## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```

The TukeyHSD plot shows that the people in the back drink a lot more than the people in the front. The plot shows those that those who sit in the middle drink less than the people in the back. The middle-front shows there is no evidence of difference in the average alcohol consumption.  

## Conclusions

There is a difference. People who sit in the back of the class are more likely to consume alcohol than those who sit in the middle and front.

